Exploring Local Explanations of Nonlinear Models Using Animated Linear Projections

### 2022-02-06 _paper.rmd

Version 0.2.0 of the package can be installed from CRAN using the following __R__ code:

```{r eval=FALSE, echo=TRUE}
install.packages("cheem", dependencies = TRUE)
library("cheem")
run_app()
```

@@

```{r eval=FALSE, echo=TRUE}
# install.packages("remotes") # if you don't have it
remotes::install_github('ModelOriented/treeshap')
```

and follow the examples provided with the package to compute the local explainers. XXX Add some information on what type of data object gets passed into cheem.

Alternatively, the cheem viewer shiny app can be directly accessed at https://ebsmonash.shinyapps.io/cheem_initial/.

>>>>

The package can be installed from GitHub using the following __R__ code:

```{r eval=FALSE, echo=TRUE}
# Install remotes if absent
if(require("remotes") == FALSE) install.packages("remotes")
remotes::install.packages("cheem", dependencies = TRUE)
library("cheem")
run_app()
```

@@

```{r eval=FALSE, echo=TRUE}
remotes::install_github('ModelOriented/treeshap')
```

Follow the examples provided with the package to compute the local explainers, (see `?cheem_ls`). The application expects the return of call from `cheem_ls()` which is then saved to an .rds file with `saveRDS()`. Alternatively, the cheem viewer shiny app can be directly accessed at https://ebsmonash.shinyapps.io/cheem_initial/.

### 2022-02-06 _paper.tex

Version 0.2.0 of the package can be installed from CRAN using the following \textbf{R} code:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{install.packages}\NormalTok{(}\StringTok{"cheem"}\NormalTok{, }\AttributeTok{dependencies =} \ConstantTok{TRUE}\NormalTok{)}
\FunctionTok{library}\NormalTok{(}\StringTok{"cheem"}\NormalTok{)}
\FunctionTok{run\_app}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# install.packages("remotes") \# if you don\textquotesingle{}t have it}
\NormalTok{remotes}\SpecialCharTok{::}\FunctionTok{install\_github}\NormalTok{(}\StringTok{\textquotesingle{}ModelOriented/treeshap\textquotesingle{}}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

and follow the examples provided with the package to compute the local explainers. XXX Add some information on what type of data object gets passed into cheem.

Alternatively, the cheem viewer shiny app can be directly accessed at \url{https://ebsmonash.shinyapps.io/cheem_initial/}.

>>>>

The package can be installed from GitHub using the following \textbf{R} code:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Install remotes if absent}
\ControlFlowTok{if}\NormalTok{(}\FunctionTok{require}\NormalTok{(}\StringTok{"remotes"}\NormalTok{) }\SpecialCharTok{==} \ConstantTok{FALSE}\NormalTok{) }\FunctionTok{install.packages}\NormalTok{(}\StringTok{"remotes"}\NormalTok{)}
\NormalTok{remotes}\SpecialCharTok{::}\FunctionTok{install.packages}\NormalTok{(}\StringTok{"cheem"}\NormalTok{, }\AttributeTok{dependencies =} \ConstantTok{TRUE}\NormalTok{)}
\FunctionTok{library}\NormalTok{(}\StringTok{"cheem"}\NormalTok{)}
\FunctionTok{run\_app}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{remotes}\SpecialCharTok{::}\FunctionTok{install\_github}\NormalTok{(}\StringTok{\textquotesingle{}ModelOriented/treeshap\textquotesingle{}}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

Follow the examples provided with the package to compute the local explainers, (see \texttt{?cheem\_ls}). The application expects the return of call from \texttt{cheem\_ls()} which is then saved to an .rds file with \texttt{saveRDS()}. Alternatively, the cheem viewer shiny app can be directly accessed at \url{https://ebsmonash.shinyapps.io/cheem_initial/}.
